On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-29 docs/mvfits_paper/mvf.tex
minor updates to text

@@

These frequencies and harmonic functions are the so-called \qnm{s}.

@@

They are the eigen-solutions of the source free linearized \ee{} (i.e. \tk{'s} equations \cite{PhysRevLett.29.1114}) for a perturbed \bh{} with final mass, $\mf$, and dimensionless final spin, $\jf$.

@@

While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in the literature, there exist minor shortcomings which we wish to address here \cite{Berti:2005ys,Berti:2014fga}.

@@

In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (See \ceqn{hlm}).

@@

@@

With this in mind, here, we will develop algorithms for the linear (polynomial and rational) modeling of scalar functions (real or complex valued) of many variables.

@@

In particular, defining ${U}_{jk} = \phi_k(\vec{x}_j)$, $f_j = f(\vec{x}_j)$ then $\vec{f} = \hat{U} \; \vec{\mu}$, implies that

>>>>

, where $\omega\lmn$ is the central frequency of the ringing, and $1/\tau\lmn$ is the damping rate.

@@

Together, these harmonic functions and frequencies constitute the \qnm{} solutions to \ee{}.

@@

Specifically, they are the eigen-solutions of the source free linearized \ee{} (i.e. \tk{'s} equations \cite{PhysRevLett.29.1114}) for a perturbed \bh{} with final mass, $\mf$, and dimensionless final spin, $\jf$.

@@

While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in the literature (e.g. \cite{Berti:2005ys,Berti:2014fga}), there exist minor shortcomings which we wish to address here.

@@

In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (via \ceqn{hlm}).

@@

Both algorithms are publicly available in \texttt{Python} via Ref. \cite{lionel_london_2018_1402516}.

@@

With this in mind, here, we will develop algorithms for the linear (polynomial and rational) modeling of scalar functions (real or complex) of many variables.

@@

In particular, defining ${U}_{jk} = \phi_k(\vec{x}_j)$, $f_j = f(\vec{x}_j)$ and $\vec{f} = \hat{U} \; \vec{\mu}$, implies that
